visitation_bias

### 2021-01-14 code/visitation_bias.Rmd
back to lappy

---
title: "visitation_bias"
author: "Doug Sponsler"
date: "12/14/2020"
output: html_document
---
# Preparations
## Packages 
```{r, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(brms)
library(lme4)
library(ggeffects)
library(sjPlot)
#library(inla)
library(bayesplot)
library(vegan)
#library(tidybayes)
library(tidyverse)
library(lubridate)
library(tidymodels)
```

>>>>

---
title: "visitation_bias"
author: "Doug Sponsler"
date: "12/14/2020"
output: html_document
---
# Preparations
## Packages 
```{r, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(brms)
library(lme4)
library(bayesplot)
library(vegan)
library(tidyverse)
library(lubridate)
library(tidymodels)
```
